---
title: "HVLC GIRFT Code Examples"
author: "NHS Transformation Unit"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true
    css: ../../config/nhs_tu_theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

source("../../requirements/packages.R")
source("load.R")
source("ENT.R")
source("General_Surgery.R")
source("Ophthalmology.R")
source("Urology.R")

```

```{r logo, echo = FALSE}

htmltools::img(src = knitr::image_uri(paste0(here(), "/images/TU_logo_large.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:5%; padding:10px;',
               width = "180px",
               heigth = "180px")

```

# Introduction
***

This document has been created to demonstrate how to extract and identify *HVLC* activity based on the criteria supplied by the Getting it Right First Time (*GIRFT*) Programme.

# Example Extract {.tabset .tabset-fade}
***

## Inpatient extract

For these examples the script in `src/data/sql_scripts/extract.sql` will need to be run within the NCDR environment and the outputs saved as `extract.xlsx` within `src/data`. The sql script used to extract the data is provided below:

```{sql, file='../sql_scripts/extract.sql', echo = TRUE, eval = FALSE}
```

<br/>

# Inpatient Specialty HVLC
***

These section look at identifying inpatient HVLC activities

## ENT {.tabset .tabset-fade}
For ENT there are five different HVLC groups that are currently defined by GIRFT. Examples of how to use the functions that have been created in this repository within the `src/data/r_scripts/ENT.R` script are given below. The final tab shows the code that has been written to create the functions to either filter or flag episodes of interest.

### Endo Sinus Surgery
The code below will filter the extracted APCE data to keep only the Endo Sinus Surgery activity.

```{r ENT Endo Sinus Filter}

ent_ess_filter <- hvlc_ent_endo_sinus_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

ent_ess_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r ENT Endo Sinus Flag}

ent_ess_flag <- hvlc_ent_endo_sinus_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Endo_sinus_Flag")) %>%
  head(n = 15)

ent_ess_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Tonsillectomy
The code below will filter the extracted APCE data to keep only the Tonsillectomy activity.

```{r ENT Tonsillectomy Filter}

ent_ton_filter <- hvlc_ent_tonsillectomy_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

ent_ton_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r ENT Tonsillectomy Flag}

ent_ton_flag <- hvlc_ent_tonsillectomy_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Tonsillectomy_Flag")) %>%
  head(n = 15)

ent_ton_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Myringoplasty
The code below will filter the extracted APCE data to keep only the Myringoplasty activity.

```{r ENT Myringoplasty Filter}

ent_myr_filter <- hvlc_ent_myringoplasty_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

ent_myr_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r ENT Myringoplasty Flag}

ent_myr_flag <- hvlc_ent_myringoplasty_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "myringoplasty_Flag")) %>%
  head(n = 15)

ent_myr_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Septoplasty and Turbinate
The code below will filter the extracted APCE data to keep only the Septoplasty & Turbinate activity.

```{r ENT Septo Turb Filter}

ent_st_filter <- hvlc_ent_septo_turb_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

ent_st_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r ENT Septo Turb Flag}

ent_st_flag <- hvlc_ent_septo_turb_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Septo_Turb_Flag")) %>%
  head(n = 15)

ent_st_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Septorhinoplasty
The code below will filter the extracted APCE data to keep only the Septorhinoplasty activity.

```{r ENT Septorhinoplasty Filter}

ent_sh_filter <- hvlc_ent_septorhino_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

ent_sh_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r ENT Septorhinoplasty Flag}

ent_sh_flag <- hvlc_ent_septorhino_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Septorhino_Flag")) %>%
  head(n = 15)

ent_sh_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### R Functions
The code below has been written to create the functions that will either filter or flag activity based on the ENT HVLC criteria:
```{r, file='ENT.R', echo = TRUE, eval = FALSE}
```

<br/>

## General Surgery {.tabset .tabset-fade}
For General Surgery there are three different HVLC groups that are currently defined by GIRFT. Examples of how to use the functions that have been created in this repository within the `src/data/r_scripts/General_Surgery.R` script are given below. The final tab shows the code that has been written to create the functions to either filter or flag episodes of interest.

### Laparoscopic cholecystectomy
The code below will filter the extracted APCE data to keep only the Laparoscopic cholecystectomy Surgery activity.

```{r Gen Surg Laparoscopic cholecystectomy Filter}

gs_lc_filter <- hvlc_gs_lc_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

gs_lc_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Gen Surg Laparoscopic cholecystectomy Flag}

gs_lc_flag <- hvlc_gs_lc_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Laparoscopic_cholecystectomy_flag")) %>%
  head(n = 15)

gs_lc_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Primary inguinal hernia repair
The code below will filter the extracted APCE data to keep only the Primary inguinal hernia repair Surgery activity.

```{r Gen Surg Primary inguinal hernia repair Filter}

gs_pihr_filter <- hvlc_gs_pihr_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

gs_pihr_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Gen Surg Primary inguinal hernia repair Flag}

gs_pihr_flag <- hvlc_gs_pihr_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Primary_inguinal_hernia_repair_flag")) %>%
  head(n = 15)

gs_pihr_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Para-umbilical hernia
The code below will filter the extracted APCE data to keep only the Para-umbilical hernia Surgery activity.

```{r Gen Surg Para-umbilical hernia Filter}

gs_puh_filter <- hvlc_gs_puh_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

gs_pihr_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Gen Surg Para-umbilical hernia Flag}

gs_puh_flag <- hvlc_gs_puh_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Para_umbilical_hernia_flag")) %>%
  head(n = 15)

gs_puh_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### R Functions
The code below has been written to create the functions that will either filter or flag activity based on the General Surgery HVLC criteria:
```{r, file='General_Surgery.R', echo = TRUE, eval = FALSE}
```

<br/>

## Ophthalmology {.tabset .tabset-fade}
For Ophthalmology there is one HVLC groups that are currently defined by GIRFT. Examples of how to use the functions that have been created in this repository within the `src/data/r_scripts/Ophthalmology.R` script are given below. The final tab shows the code that has been written to create the functions to either filter or flag episodes of interest.

### Low complexity cataract surgery
The code below will filter the extracted APCE data to keep only the Low Complexity Cataract Surgery activity.

```{r Ophth Low Complexity Cataract Surgery Filter}

ophth_lccs_filter <- hvlc_ophth_lccs_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

ophth_lccs_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Ophth Low Complexity Cataract Surgery Flag}

ophth_lccs_flag <- hvlc_ophth_lccs_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Low_complexity_cataract_surgery_flag")) %>%
  head(n = 15)

ophth_lccs_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### R Functions
The code below has been written to create the functions that will either filter or flag activity based on the Ophthalmology HVLC criteria:
```{r, file='Ophthalmology.R', echo = TRUE, eval = FALSE}
```

<br/>

## Urology {.tabset .tabset-fade}
For Urology there are five different HVLC groups that are currently defined by GIRFT. Examples of how to use the functions that have been created in this repository within the `src/data/r_scripts/Urology.R` script are given below. The final tab shows the code that has been written to create the functions to either filter or flag episodes of interest.

### Bladder outflow obstruction
The code below will filter the extracted APCE data to keep only the Bladder Outflow Obstruction activity.

```{r Urology Bladder Outflow Obstruction Filter}

urology_boo_filter <- hvlc_urology_boo_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

urology_boo_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```
<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Urology Bladder Outflow Obstruction Flag}

urology_boo_flag <- hvlc_urology_boo_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Bladder_outflow_obstruction_flag")) %>%
  head(n = 15)

urology_boo_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```
<br/>

### Bladder tumour resection (TURBT)
The code below will filter the extracted APCE data to keep only the Bladder Tumour Resection (TURBT) activity.

```{r Urology Bladder tumour resection Filter}

urology_btr_filter <- hvlc_urology_btr_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

urology_btr_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Urology Bladder tumour resection Flag}

urology_btr_flag <- hvlc_urology_btr_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Bladder_tumour_resection_flag")) %>%
  head(n = 15)

urology_btr_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Cystoscopy plus
The code below will filter the extracted APCE data to keep only the Cystoscopy plus activity.

```{r Urology Cystoscopy plus Filter}

urology_cyst_filter <- hvlc_urology_cyst_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

urology_cyst_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Urology Cystoscopy plus Flag}

urology_cyst_flag <- hvlc_urology_cyst_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Cystoscopy_plus_flag")) %>%
  head(n = 15)

urology_cyst_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Ureteroscopy and stent management
The code below will filter the extracted APCE data to keep only the Ureteroscopy And Stent Management activity.

```{r Urology Ureteroscopy and stent management Filter}

urology_usm_filter <- hvlc_urology_usm_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

urology_usm_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Urology Ureteroscopy and stent management Flag}

urology_usm_flag <- hvlc_urology_usm_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Ureteroscopy_and_stent_management_flag")) %>%
  head(n = 15)

urology_usm_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### Minor peno-scrotal surgery
The code below will filter the extracted APCE data to keep only the Minor Peno-Scrotal Surgery activity.

```{r Urology Minor peno-scrotal surgery Filter}

urology_mpss_filter <- hvlc_urology_mpss_filter(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All"))

urology_mpss_filter %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

Alternatively, an additional field can be created to flag which records are identified:
```{r Urology Minor peno-scrotal surgery Flag}

urology_mpss_flag <- hvlc_urology_mpss_flag(extract) %>%
  select(c("APCE_Ident", "Main_Specialty_Code", "Treatment_Function_Code", "Der_Diagnosis_All", "Der_Procedure_All", "Minor_peno_scrotal_surgery_flag")) %>%
  head(n = 15)

urology_mpss_flag %>%
  kable(format = "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "200px")

```

<br/>

### R Functions
The code below has been written to create the functions that will either filter or flag activity based on the Urology HVLC criteria:
```{r, file='Urology.R', echo = TRUE, eval = FALSE}
```


















