---
title: "HVLC GIRFT Code Examples"
author: "NHS Transformation Unit"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true
    css: ../../config/nhs_tu_theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

source("../../requirements/packages.R")
source("load.R")

```

```{r logo, echo = FALSE}

htmltools::img(src = knitr::image_uri(paste0(here(), "/images/TU_logo_large.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:5%; padding:10px;',
               width = "180px",
               heigth = "180px")

```

# Introduction
This document has been created to demonstrate how to extract and identify *HVLC* activity based on the criteria supplied by the Getting it Right First Time (*GIRFT*) Programme.

# Example Extract
For these examples the script in `src/data/sql_scripts/extract.sql` will need to be run within the NCDR environment and the outputs saved as `extract.xlsx` within `src/data`. The sql script used to extract the data is provided below:

```{r sql_extract, include_sql = FALSE, eval = TRUE}

sql_script <- readLines("../sql_scripts/extract.sql")
cat(sql_script, sep = "\n")

```

